\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}

\name{Daniel Jaramillo Calderon}
\address{ \faMobile \hspace{0.1cm} +1(604) 753 8817 \\ \faEnvelopeO \hspace{0.1cm} \href{mailto:jaramillocalderondc@gmail.com}{jaramillocalderondc@gmail.com} }
\address{ \faHome \hspace{0.1cm} 6000 Iona Drive. Vancouver, BC}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Education}
    {\bf Ph.D. in Economics } {- student} \hfill {\em Sept 2019 - Present} \\ 
    { The University of British Columbia }\\ 
    {\bf M.A. in Economics } \hfill {\em Sept 2017 - Aug 2018} \\ 
    { University of British Columbia } \\
    {\bf B.Sc. in Economics } \hfill {\em Sept 2011 - May 2015} \\ 
    { Pontificia Universidad Católica del Ecuador } \\
  \end{rSection}
  
  \begin{rSection}{Experience}
    
    \begin{rSubsection}{Teaching Assistantships}{}{}{}
    \item {\em Introductory Macroeconomics}. UBC. Vancouver, Canada \hfill{\em Jan 2021 - Apr 2021}
    \item {\em Introductory Microeconomics}. UBC. Vancouver, Canada \hfill{\em Sept 2020 - Dec 2020}
    \item {\em Data Science Applications}. UBC. Vancouver, Canada \hfill{\em Sept 2020 - Dec 2020}
    \item {\em Introductory Microeconomics}. UBC. Vancouver, Canada \hfill{\em Sept 2017 - Apr 2018}
    \item {\em Econometrics}. PUCE. Quito, Ecuador \hfill{\em Jun 2016 - Mar 2017}
    \item {\em Statistics}. PUCE. Quito, Ecuador \hfill{\em Jun 2016 - Mar 2017}
    \item {\em Industrial Organization}. PUCE. Quito, Ecuador \hfill{\em Jan 2014 - Dec 2014}
    \item {\em Intermediate Microeconomics}. PUCE. Quito, Ecuador \hfill{\em Jan 2014 - Dec 2014}
    \end{rSubsection}
  
    \begin{rSubsection}{Research}{}{}{}
    \item {\em Research Assistant} for Phillip Keefer \hfill{\em Sept 2018 - Aug 2019}
    \item {\em Research Assistant} for Sergio Guerra \hfill{\em Jun 2016 - May 2017}
    \item {\em Research Assistant} for Lenin Parreño \hfill{\em Jan 2014 - Dec 2014}
    \end{rSubsection}

    \begin{rSubsection}{Professional}{}{}{}
    \item {\em Research Fellow} at Secretary of National Planning and Development Strategy \hfill{\em Jun 2016 - Jun 2017}
    \item {\em Market Analyst} at Superintendence for the Control of the Market Power \hfill{\em Nov 2014 - May 2016}
    \item {\em Intern} at Moore Stephens \hfill{\em May 2014 - Jun 2014}
    \end{rSubsection}
  
  \end{rSection}
  
\begin{rSection}{Awards and Fellowships}
  \begin{rSubsection}{}{}{}{}
    \item ­	CIDE Doctoral Fellowship, Vancouver School of Economics (UBC), 2019-2020.
    \item ­	CIDE Masters Fellowship, Vancouver School of Economics (UBC), 2017-2018.
    \item ­	Universities of Excellence Scholarship, Ministry of Education (Ecuador), 2017 (declined).
    \item ­	RCM Fellowship, Pontificia Universidad Católica del Ecuador, 2014.
  \end{rSubsection}
\end{rSection}

  \begin{rSection}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Programming & Julia, Python \\
      Statistical Packages & Stata, R, SPSS \\
      Markup & \LaTeX, Markdown
    \end{tabular}
  \end{rSection}

\end{document}
